%%
%% Title Page — Journal of Agricultural, Biological and Environmental Statistics (Springer)
%%
\documentclass[12pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[american]{babel}
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

\begin{document}

\begin{center}

{\LARGE\bfseries Machine Learning Readiness to Support Agroecological\\[4pt]
Transitions in Traditional Agricultural Systems}

\vspace{24pt}

{\large
Catuxe Varjão de Santana Oliveira\textsuperscript{a},\quad
Luiz Diego Vidal Santos\textsuperscript{b,*},\quad
Paulo Roberto Gagliardi\textsuperscript{a},\\[6pt]
Renisson Neponuceno de Araújo Filho\textsuperscript{c},\quad
Tânia Cristina Azevedo\textsuperscript{b},\\[6pt]
Gustavo da Silva Quirino\textsuperscript{a},\quad
Alceu Pedrotti\textsuperscript{a},\quad
Francisco Sandro Rodrigues Holanda\textsuperscript{a}
}

\vspace{18pt}

\end{center}

\noindent
\textsuperscript{a}\,Universidade Federal de Sergipe (UFS), Av.\ Marechal Rondon, s/n, Jardim Rosa Elze, São Cristóvão, SE 49100-000, Brazil\\[4pt]
\textsuperscript{b}\,Universidade Estadual de Feira de Santana (UEFS), Av.\ Transnordestina, s/n, Novo Horizonte, Feira de Santana, BA 44036-900, Brazil\\[4pt]
\textsuperscript{c}\,Universidade Federal Rural de Pernambuco (UFRPE), Rua Dom Manuel de Medeiros, s/n, Dois Irmãos, Recife, PE 52171-900, Brazil

\vspace{18pt}

\noindent
\textbf{*\,Corresponding author:}\\
Luiz Diego Vidal Santos\\
Universidade Estadual de Feira de Santana (UEFS)\\
Av.\ Transnordestina, s/n, Novo Horizonte\\
Feira de Santana, BA 44036-900, Brazil\\
E-mail: ldvsantos@uefs.br

\vspace{24pt}

\noindent
\textbf{Word count:} $\sim$8\,000 (main text, excluding references, tables, and figure captions)\\[4pt]
\textbf{Number of figures:} 11 (Figs.\ 1--8b)\\[4pt]
\textbf{Number of tables:} 1\\[4pt]
\textbf{Supplementary material:} References of the Meta-Analysis (separate document)

\vspace{24pt}
\hrule
\vspace{12pt}

\noindent\textbf{Acknowledgments}\\[4pt]
The authors thank the Universidade Federal de Sergipe (UFS), the Universidade Estadual de Feira de Santana (UEFS), and the Instituto Federal de Sergipe (IFS) for the institutional and infrastructural support that enabled this research.

\vspace{12pt}

\noindent\textbf{Funding}\\[4pt]
This research did not receive any specific grant from funding agencies in the public, commercial, or not-for-profit sectors.

\vspace{12pt}

\noindent\textbf{CRediT authorship contribution statement}\\[4pt]
\textbf{Catuxe Varjão de Santana Oliveira:} Conceptualization, Investigation, Writing -- original draft, Project administration.
\textbf{Luiz Diego Vidal Santos:} Conceptualization, Methodology, Software, Formal analysis, Investigation, Data curation, Writing -- original draft, Visualization.
\textbf{Paulo Roberto Gagliardi:} Writing -- review \& editing, Supervision.
\textbf{Renisson Neponuceno de Araújo Filho:} Writing -- review \& editing.
\textbf{Tânia Cristina Azevedo:} Writing -- review \& editing.
\textbf{Gustavo da Silva Quirino:} Writing -- review \& editing.
\textbf{Alceu Pedrotti:} Writing -- review \& editing.
\textbf{Francisco Sandro Rodrigues Holanda:} Writing -- review \& editing, Supervision.

\vspace{12pt}

\noindent\textbf{Declaration of competing interests}\\[4pt]
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

\end{document}
